---
title: "Plot for covid-19"
author: "Jin Ge"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css: styles_Dashboard.css
runtime: shiny
---

```{r setup, include=FALSE}

library(tidyverse)
library(flexdashboard)
library(shiny)
library(plotly)

# load the data
## the data is covid_date_by_zip
covid_dat <- read.csv("covid_date_by_zip.csv") %>% 
  select(-X) %>% arrange(modzcta, date) %>% select(modzcta, date, everything()) %>% 
  drop_na(modzcta) 

## the social status data
social_dat <- read.csv("social_dat.csv") %>% select(-X)

```

COVID-19 data for NYC as a whole
=====================================

Column {.sidebar}
-----------------------------------------------------------------------
```{r sidebar_whole}
data_category <- c("case number", "death number", "total number", "positive percentage", "case rate", "death rate")

selectInput("data_category", label = h3("Choose data category"),
            choices = as.list(data_category), selected = "case number")

```

Column {.tabset .tabset-fade .tabset-pills}
-----------------------------------------------------------------------
### <span style="color:#69899f"> **NYC COVID-19 data** </span>

```{r NYC_as_whole}

renderPlotly(if (input$data_category == "case number"){
  covid_dat %>% group_by(date) %>% summarize(number_of_cases = sum(dif_case)) %>% 
  select(date, number_of_cases) %>% 
  plot_ly(x = ~date, y = ~number_of_cases, type = "bar")
}else if (input$data_category == "death number"){
  covid_dat %>% group_by(date) %>% summarize(number_of_death = sum(dif_death)) %>% 
  select(date, number_of_death) %>% 
  plot_ly(x = ~date, y = ~number_of_death, type = "bar")
}else if (input$data_category == "total number"){
  covid_dat %>% group_by(date) %>% summarize(total_number_of_tests = sum(dif_total)) %>% 
  select(date, total_number_of_tests) %>% 
  plot_ly(x = ~date, y = ~total_number_of_tests, type = "bar")
}else if (input$data_category == "positive percentage"){
  covid_dat %>% group_by(date) %>% summarize(positive_percentage = sum(dif_case)/sum(dif_total)) %>% 
  select(date, positive_percentage) %>% 
  plot_ly(x = ~date, y = ~positive_percentage, type = "bar")
}else if (input$data_category == "case rate"){
  covid_dat %>% group_by(date) %>% summarize(total_case_rate = sum(dif_case_rate)) %>% 
  select(date, total_case_rate) %>% 
  plot_ly(x = ~date, y = ~total_case_rate, type = "bar")
}else if (input$data_category == "death rate"){
  covid_dat %>% group_by(date) %>% summarize(total_death_rate = sum(dif_death_rate)) %>% 
  select(date, total_death_rate) %>% 
  plot_ly(x = ~date, y = ~total_death_rate, type = "bar")
})


```


Data for NYC across zip codes by date
=====================================

Column {.sidebar}
-----------------------------------------------------------------------
```{r sidebar_each}
zipcode <- covid_dat %>% distinct(modzcta) %>% pull()

selectInput("zipcode", label = h3("NYC zip code"),
            choices = as.list(zipcode), selected = 10001)

```

Column {.tabset .tabset-fade .tabset-pills}
-----------------------------------------------------------------------
### <span style="color:#69899f"> **Cases number** </span>

```{r case_plot_by_day_across_zipcode}
renderPlotly({
  indx <- which(zipcode == input$zipcode)

  covid_dat %>% filter(modzcta == zipcode[[indx]]) %>% 
               plot_ly(x = ~date, y = ~dif_case, type = "bar")%>% 
      layout( 
          xaxis = list(
            title = "Date",
            dtick = 1,
            tick0 = 04/03/2020,
            tickmode = "linear"),
          yaxis = list(
            title = "Number of cases",
            dtick = 5,
            tick0 = 0,
            tickmode = "linear"))
}
)

```

### <span style="color:#69899f"> **Death number** </span>

```{r death_plot_by_day_across_zipcode}
renderPlotly({
  indx <- which(zipcode == input$zipcode)

  covid_dat %>% filter(modzcta == zipcode[[indx]]) %>% 
               plot_ly(x = ~date, y = ~dif_death, type = "bar") %>% 
      layout( 
          xaxis = list(
            title = "Date",
            dtick = 1,
            tick0 = 04/03/2020,
            tickmode = "linear"),
          yaxis = list(
            title = "Number of death",
            dtick = 1,
            tick0 = 0,
            tickmode = "linear"))
}
)

```

### <span style="color:#69899f"> **Total number of tests** </span>

```{r total_plot_by_day_across_zipcode}
renderPlotly({
  indx <- which(zipcode == input$zipcode)

  covid_dat %>% filter(modzcta == zipcode[[indx]]) %>% 
               plot_ly(x = ~date, y = ~dif_total, type = "bar")%>% 
      layout( 
          xaxis = list(
            title = "Date",
            dtick = 1,
            tick0 = 04/03/2020),
          yaxis = list(
            title = "Total number of tests",
            dtick = 500,
            tick0 = 0,
            tickmode = "linear"))
}
)

```

### <span style="color:#69899f"> **Positive percentage** </span>

```{r pospercent_plot_by_day_across_zipcode}
renderPlotly({
  indx <- which(zipcode == input$zipcode)

  covid_dat %>% filter(modzcta == zipcode[[indx]]) %>% 
               plot_ly(x = ~date, y = ~dif_per_positive, type = "bar")%>% 
      layout( 
          xaxis = list(
            title = "Date",
            dtick = 1,
            tick0 = 04/03/2020,
            tickmode = "linear"),
          yaxis = list(
            title = "Positive percentage"))
}
)

```

### <span style="color:#69899f"> **Case rate** </span>

```{r case_rate_plot_by_day_across_zipcode}
renderPlotly({
  indx <- which(zipcode == input$zipcode)

  covid_dat %>% filter(modzcta == zipcode[[indx]]) %>% 
               plot_ly(x = ~date, y = ~dif_case_rate, type = "bar")%>% 
      layout( 
          xaxis = list(
            title = "Date",
            dtick = 1,
            tick0 = 04/03/2020,
            tickmode = "linear"),
          yaxis = list(
            title = "Case rate",
            dtick = 1,
            tick0 = 0,
            tickmode = "linear"))
}
)

```

### <span style="color:#69899f"> **Death rate** </span>

```{r death_rate_plot_by_day_across_zipcode}
renderPlotly({
  indx <- which(zipcode == input$zipcode)

  covid_dat %>% filter(modzcta == zipcode[[indx]]) %>% 
               plot_ly(x = ~date, y = ~dif_death_rate, type = "bar")%>% 
      layout( 
          xaxis = list(
            title = "Date",
            dtick = 1,
            tick0 = 04/03/2020,
            tickmode = "linear"),
          yaxis = list(
            title = "Death rate",
            dtick = 1,
            tick0 = 0,
            tickmode = "linear"))
}
)

```

### <span style="color:#69899f"> **Discription** </span>

<br><br>

* **Case number**: the number of cases in each zipcode by day
* **Death number**: the number of death in each zipcode by day
* **Total number of tests**: the total number of tests in each zipcode by day
* **Positive percentage**: the positive percentage of COVID-19 in each zipcode by day (calculated by case number divided by total number of testing)
* **Case rate**: the case rate of COVID-19 in each zipcode by day (the number of cases in every 100,000 population in NYC)
* **Death rate**: the death rate of COVID-19 in each zipcode by day (the number of death in every 100,000 population in NYC)

Note: 

* The plot demonstrates abnormal data on April 27. We may need to consider a way to deal with it.

* The values of positive percentage are quite abnormal with many values further greater than 1.

